Title

### 2024-04-04 latex/draft/draft.tex
add error table

    # Get sample size
    n <- nrow(X)
    # Initialize empty vector
    params <- c()
    # Perform B iterations
    for (b in 1:B) {
        # Get errors
        errs <- sample(errors, size=n, replace=TRUE)
        # Get fitted values
        yhat <- fitted(model)
        # Get simulated y
        ystar <- yhat + errs
        # round up negative values
        ystar <- pmax(rep(0, n), ystar)
        # Turn into DataFrame
        sim_data <- data.frame(protests=ystar, X)
        # Fit the model with the simulated data
        paramboot_model <- glm.nb(protests ~., data=sim_data, init.theta = 5)
        boot_params <- coef(paramboot_model)
        params <- rbind(params, boot_params)
    }
    return(params)
}
\end{lstlisting}
\subsubsection*{Results}
\begin{table}[hbt!]
    \centering
    \begin{tabular}{|l|c|c|c|c|c|c|}
      \hline
     & mean & sd & 2.5\% & 50\% & 97.5\% & sig \\ 
      \hline
    intercept & 3.68 & 0.51 & 2.68 & 3.68 & 4.69 & TRUE \\ 
      Spr & -0.07 & 0.08 & -0.23 & -0.07 & 0.10 & FALSE \\ 
      Sum & -0.55 & 0.09 & -0.72 & -0.55 & -0.38 & TRUE \\ 
      Win & -0.23 & 0.09 & -0.41 & -0.23 & -0.05 & TRUE \\ 
      BC & 0.82 & 0.16 & 0.51 & 0.82 & 1.14 & TRUE \\ 
      M & -1.92 & 0.92 & -3.75 & -1.91 & -0.11 & TRUE \\ 
      NB & -2.63 & 1.05 & -4.72 & -2.63 & -0.57 & TRUE \\ 
      NL & -3.08 & 1.11 & -5.31 & -3.06 & -0.89 & TRUE \\ 
      NT & -5.41 & 1.27 & -7.92 & -5.39 & -2.91 & TRUE \\ 
      NS & -2.42 & 1.00 & -4.39 & -2.41 & -0.46 & TRUE \\ 
      N & -5.01 & 1.27 & -7.52 & -5.01 & -2.53 & TRUE \\ 
      O & 5.61 & 2.45 & 0.80 & 5.59 & 10.51 & TRUE \\ 
      PEI & -4.13 & 1.22 & -6.54 & -4.12 & -1.73 & TRUE \\ 
      Q & 2.20 & 0.93 & 0.36 & 2.19 & 4.07 & TRUE \\ 
      S & -2.59 & 0.94 & -4.46 & -2.57 & -0.75 & TRUE \\ 
      Y & -4.15 & 1.25 & -6.61 & -4.14 & -1.71 & TRUE \\ 
      retail & -1.86 & 1.07 & -3.98 & -1.85 & 0.23 & FALSE \\ 
       \hline
    \end{tabular}
\end{table}

>>>>

    # Get sample size
    n <- nrow(X)
    # Initialize empty vector
    params <- c()
    # Perform B iterations
    for (b in 1:B) {
        # Get errors
        errs <- sample(errors, size=n, replace=TRUE)
        # Get fitted values
        yhat <- fitted(model)
        # Get simulated y
        ystar <- yhat + errs
        # round up negative values
        ystar <- pmax(rep(0, n), ystar)
        # Turn into DataFrame
        sim_data <- data.frame(protests=ystar, X)
        # Fit the model with the simulated data
        paramboot_model <- glm.nb(protests ~., data=sim_data, init.theta = 5)
        boot_params <- coef(paramboot_model)
        params <- rbind(params, boot_params)
    }
    return(params)
}
\end{lstlisting}
\subsubsection*{Results}
\begin{table}[hbt!]
    \centering
    \begin{tabular}{|l|c|c|c|c|c|c|}
      \hline
     & mean & sd & 2.5\% & 50\% & 97.5\% & sig \\ 
     \hline
     intercept & 3.66 & 0.05 & 3.56 & 3.66 & 3.76 & TRUE \\ 
       seasonSpring & -0.07 & 0.01 & -0.09 & -0.07 & -0.04 & TRUE \\ 
       seasonSummer & -0.56 & 0.02 & -0.59 & -0.56 & -0.53 & TRUE \\ 
       seasonWinter & -0.24 & 0.01 & -0.27 & -0.24 & -0.21 & TRUE \\ 
       BC & 0.82 & 0.02 & 0.78 & 0.82 & 0.86 & TRUE \\ 
       M & -1.89 & 0.09 & -2.07 & -1.89 & -1.71 & TRUE \\ 
       NB & -2.61 & 0.11 & -2.83 & -2.61 & -2.40 & TRUE \\ 
       NL & -3.07 & 0.12 & -3.30 & -3.07 & -2.83 & TRUE \\ 
       NT & -5.20 & 0.28 & -5.80 & -5.18 & -4.70 & TRUE \\ 
       NS & -2.40 & 0.10 & -2.60 & -2.40 & -2.20 & TRUE \\ 
       N & -4.96 & 0.25 & -5.50 & -4.95 & -4.51 & TRUE \\ 
       O & 5.54 & 0.24 & 5.07 & 5.54 & 6.02 & TRUE \\ 
       PEI & -4.16 & 0.18 & -4.51 & -4.15 & -3.83 & TRUE \\ 
       Q & 2.17 & 0.09 & 1.99 & 2.17 & 2.35 & TRUE \\ 
       S & -2.58 & 0.10 & -2.78 & -2.57 & -2.38 & TRUE \\ 
       Y & -4.18 & 0.17 & -4.54 & -4.18 & -3.85 & TRUE \\ 
       retail & -1.82 & 0.10 & -2.03 & -1.82 & -1.62 & TRUE \\ 
        \hline
    \end{tabular}
\end{table}
